\section{C++}
\subsection{template}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/1. template.cpp}
\hrulefill
\subsection{random}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/2. random.cpp}
\hrulefill
\subsection{gp\_hash}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/3. gp_hash.cpp}
\hrulefill
\subsection{pbds}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/4. pbds.cpp}
\hrulefill
\subsection{debug}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/5. debug.cpp}
\hrulefill
\subsection{stress}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/6. stress.cpp}
\hrulefill
\subsection{vscode}
\raggedbottom\lstinputlisting[style=cpp]{code/c++/7. vscode.cpp}
\hrulefill

\section{Dsa}
\subsection{KMP}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/1. KMP.cpp}
\hrulefill
\subsection{Hashing}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/2. Hashing.cpp}
\hrulefill
\subsection{BigInteger}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/3. BigInteger.cpp}
\hrulefill
\subsection{Kadane}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/4. Kadane.cpp}
\hrulefill
\subsection{Segement\_tree}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/5. Segement_tree.cpp}
\hrulefill
\subsection{Fenwick\_tree}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/6. Fenwick_tree.cpp}
\hrulefill
\subsection{Segment\_tree\_lazy}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/7. Segment_tree_lazy.cpp}
\hrulefill
\subsection{Trie}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/8.Trie.cpp}
\hrulefill
\subsection{DSU}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/9. DSU.cpp}
\hrulefill
\subsection{HLD}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/10. HLD.cpp}
\hrulefill
\subsection{Manacher}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/11. Manacher.cpp}
\hrulefill
\subsection{2D prefix Sum}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/12. 2D prefix Sum.cpp}
\hrulefill
\subsection{CRT}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/14. CRT.cpp}
\hrulefill
\subsection{Intersect two arithmetic progression}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/15. Intersect two arithmetic progression.cpp}
\hrulefill
\subsection{Find nth value in a recurrence relation in O(logn}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/16. Find nth value in a recurrence relation in O(logn.cpp}
\hrulefill
\subsection{All\_solution\_of\_ax+by\_equal\_c}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/17. All_solution_of_ax+by_equal_c.cpp}
\hrulefill
\subsection{all soln of linear eq}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/18. all soln of linear eq.cpp}
\hrulefill
\subsection{Subset sum sqrt(n)}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/19. Subset sum sqrt(n).cpp}
\hrulefill
\subsection{small giant (a\textasciicircum{}x = b mod m, find x, given other)}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/20. small giant (a^x = b mod m, find x, given other).cpp}
\hrulefill
\subsection{Gaussian Elimination}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/21. Gaussian Elimination.cpp}
\hrulefill
\subsection{Grundy}
\raggedbottom\lstinputlisting[style=cpp]{code/dsa/22. Grundy.cpp}
\hrulefill

\section{Dynamic Programming}
\subsection{LCS}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/1. LCS.cpp}
\hrulefill
\subsection{MCM}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/2. MCM.cpp}
\hrulefill
\subsection{LIS\_length}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/3. LIS_length.cpp}
\hrulefill
\subsection{LCIS}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/4. LCIS.cpp}
\hrulefill
\subsection{SOS DP}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/5. SOS DP.cpp}
\hrulefill
\subsection{BS optimization}
\raggedbottom\lstinputlisting[style=cpp]{code/dynamic-programming/6. BS optimization.cpp}
\hrulefill

\section{Graph}
\subsection{Dijkstra}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/1. Dijkstra.cpp}
\hrulefill
\subsection{BellmanFord}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/2. BellmanFord.cpp}
\hrulefill
\subsection{FloydWarshall}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/3. FloydWarshall.cpp}
\hrulefill
\subsection{Toposort}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/4. Toposort.cpp}
\hrulefill
\subsection{Kruskal}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/5. Kruskal.cpp}
\hrulefill
\subsection{Prims}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/6. Prims.cpp}
\hrulefill
\subsection{LCA}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/7. LCA.cpp}
\hrulefill
\subsection{Rerooting}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/8. Rerooting.cpp}
\hrulefill
\subsection{Centroid\_Tree}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/9. Centroid_Tree.cpp}
\hrulefill
\subsection{Euler\_ckt}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/9. Euler_ckt.cpp}
\hrulefill
\subsection{Min Cost Max Flow}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/10. Min Cost Max Flow.cpp}
\hrulefill
\subsection{SCC}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/11. SCC.cpp}
\hrulefill
\subsection{0-1 BFS}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/12. 0-1 BFS.cpp}
\hrulefill
\subsection{Hull}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/13. Hull.cpp}
\hrulefill
\subsection{Dynamic Hull}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/14. Dynamic Hull.cpp}
\hrulefill
\subsection{Count SImple Cycle}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/15. Count SImple Cycle.cpp}
\hrulefill
\subsection{Count SImple Cycle}
\raggedbottom\lstinputlisting[style=cpp]{code/graph/15. Count SImple Cycle.cpp}
\hrulefill

\section{Misc}
\subsection{Max Pos and Next Greater}
\raggedbottom\lstinputlisting[style=cpp]{code/misc/1. Max Pos and Next Greater.cpp}
\hrulefill
\subsection{Knight Move}
\raggedbottom\lstinputlisting[style=cpp]{code/misc/2. Knight Move.cpp}
\hrulefill
\subsection{MatrixExpo}
\raggedbottom\lstinputlisting[style=cpp]{code/misc/3. MatrixExpo.cpp}
\hrulefill
\subsection{Ternary Search}
\raggedbottom\lstinputlisting[style=cpp]{code/misc/4. Ternary Search.cpp}
\hrulefill
\subsection{Ternary Search}
\raggedbottom\lstinputlisting[style=cpp]{code/misc/4. Ternary Search.cpp}
\hrulefill

\section{Number Theory}
\subsection{Leap\_year}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/1. Leap_year.cpp}
\hrulefill
\subsection{Two Line Intersection}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/2. Two Line Intersection.cpp}
\subsection{Two Line Intersection}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/2. Two Line Intersection.cpp}
\hrulefill
\subsection{Binary\_exponentiation}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/3. Binary_exponentiation.cpp}
\hrulefill
\subsection{Count\_divisor}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/4. Count_divisor.cpp}
\hrulefill
\subsection{Check\_prime}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/5. Check_prime.cpp}
\hrulefill
\subsection{SPF}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/6. SPF.cpp}
\hrulefill
\subsection{Seive}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/7. Seive.cpp}
\hrulefill
\subsection{Optimize\_seive}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/8. Optimize_seive.cpp}
\hrulefill
\subsection{nth\_prime\_number}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/9. nth_prime_number.cpp}
\hrulefill
\subsection{nCr}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/10. nCr.cpp}
\hrulefill
\subsection{Factorial\_mod}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/11. Factorial_mod.cpp}
\hrulefill
\subsection{PHI}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/12. PHI.cpp}
\hrulefill
\subsection{Catalan}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/13. Catalan.cpp}
\hrulefill
\subsection{Extended\_GCD}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/14. Extended_GCD.cpp}
\hrulefill
\subsection{Large Mod}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/15. Large Mod.cpp}
\hrulefill
\subsection{Factorial\_Divisor}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/16. Factorial_Divisor.cpp}
\hrulefill
\subsection{Number\_conversion}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/17. Number_conversion.cpp}
\hrulefill
\subsection{Number\_of\_1\_in\_bit\_till\_N}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/18. Number_of_1_in_bit_till_N.cpp}
\hrulefill
\subsection{Disarrangement}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/19. Disarrangement.cpp}
\hrulefill
\subsection{Millar\_Rabin}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/20. Millar_Rabin.cpp}
\hrulefill
\subsection{Modular\_operation}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/21. Modular_operation.cpp}
\hrulefill
\subsection{MSLCM}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/22. MSLCM.cpp}
\hrulefill
\subsection{Find numbers in between [L, R] which are divisible by all Array elements}
\raggedbottom\lstinputlisting[style=cpp]{code/number_theory/23. Find numbers in between [L, R] which are divisible by all Array elements.cpp}
\hrulefill

